On exponential sums arising from the classical doubling method

### 2025-04-10 main.tex
Moving multiplicativity to appendix

\elad{TODO: work on section}

@@

This theorem was proved in \cite{GirschZelingher2025} under the assumption that $\pi' \subset \Ind{P}{H'}{\tau' \overline{\otimes} \pi''}$, where $\pi''$ is an irreducible cuspidal representation of $H''$ and $\tau'$ is an irreducible representation of $\GL_{k'}\left(\finiteField\right)$ such that $\chi$ nor $\minusInvolution{\chi}$ appear in the cuspidal support of $\tau''$. \elad{TODO: check the exact condition. The Gauss sums appearing here suggest that we should replace $\chi$ with $\involution{\chi}$ and $\minusInvolution{\chi}$ with $\chi^{-1}$}

@@

>>>>

@@

This theorem follows from the results of \cite{GirschZelingher2025}. See \Cref{appendix:multiplicativity-of-jacobi-sums} for more information.

@@

\section{Multiplicativity of Jacobi sums} \label{appendix:multiplicativity-of-jacobi-sums}
\elad{TODO: Work on appendix}

\Cref{thm:multiplicativity-in-terms-of-gauss-sums} was proved in \cite{GirschZelingher2025} under the assumption that $\pi' \subset \Ind{P}{H'}{\tau' \overline{\otimes} \pi''}$, where $\pi''$ is an irreducible cuspidal representation of $H''$ and $\tau'$ is an irreducible representation of $\GL_{k'}\left(\finiteField\right)$ such that $\chi^{-1}$ nor $\involution{\chi}$ appear in the cuspidal support of $\tau'$.
